Jug: Software for Reproducible Computation In Python

### 2016-10-29 paper.tex
ENH Minor text improvements

\section*{Abstract}
As computational pipelines become a bigger part of science, it is important to
ensure that the results are reproducible. All developed software should be able
to be run automatically without any user intervention.

In addition to being valuable to the wider community, which may wish to
reproduce or extend a published analysis, reproducible research practices allow
for better control over the project by the authors themselves. For example, if
necessary parameters to run a pipeline are kept separately from the code that
implements it (in some instance even in mind of the researcher), this leads to
error-prone analysis and opens up the possibility that when the results are to
be written up for publication, the researcher will no longer be able to even
completely describe the process that led to them.

For large projects, the use of multiple processors (either in the same machine
or distributed across a cluster) is necessary to obtain results in a useful
time frame. Furthermore, it is often the case that, as the project evolves, it
becomes necessary to save intermediate results while down-stream analyses are
designed (or redesigned) and implemented. Under many frameworks, this causes
having a single point of entry (often in the form of a single script or a
single main programme) for the computation becomes increasingly difficult.

@@

The typical ad hoc solution to this problem is to save intermediate files.
Often the design of the computation itself takes several iterations as
intermediate steps are improved. Thus, some intermediate results need to be
recomputed. This involves a great amount of human management of the state of
the computation, breaking it up into pieces, and issuing jobs on the cluster.

@@

@@

Execution is the command used for running the tasks. It performs a more complex
version of this loop:

@@

The status command prints out a summary of the status of all of the tasks.
Figure~\ref{fig:jug-status-output} shows the output of this command using the
example jugfile above. We assume that the jugfile was called \code{images.py}
on disk and that there were 20~images in the directory. We can see that there
are 20~tasks ready to run, while the \code{mean} task is still waiting for the
results of the other tasks.

@@

It is still necessary to manually invalidate tasks. An alternative, was to have
the code which implements the task be taken into account while computing the
hash. While this would add another layer of protection, it would still be
possible to make mistakes. If the function depended on other functions,
especially if this was done in a dynamic way, it could be hard to discover all
dependencies (cf.\ sumatra~\footnote{Sumatra is a tool to collect all
dependencies that are necessary to run a particular computation. Its webpage is
located at \url{http://neuralensemble.org/trac/sumatra}.}). Additionally, even
minute refactoring of the code would lead to over eager recomputation. This
could make the developer wary of making improvements in their code, resulting
in overall worse code.

>>>>

\section*{Abstract}
As computational pipelines become a bigger part of science, it is important to
ensure that the results are reproducible, a concern which has come to the fore
in recent years. All developed software should be able to be run automatically
without any user intervention.

In addition to being valuable to the wider community, which may wish to
reproduce or extend a published analysis, reproducible research practices allow
for better control over the project by the authors themselves. For example, if
necessary parameters to run a pipeline are kept separately from the code that
implements it, this leads to error-prone analysis and opens up the possibility
that when the results are to be written up for publication, the researcher will
no longer be able to even completely describe the process that led to them.

For large projects, the use of multiple computational ccores (either in the
same machine or distributed across a cluster) is necessary to obtain results in
a useful time frame. Furthermore, it is often the case that, as the project
evolves, it becomes necessary to save intermediate results while down-stream
analyses are designed (or redesigned) and implemented. Under many frameworks,
this causes having a single point of entry (often in the form of a single
script or a single main programme) for the computation becomes increasingly
difficult.

@@

The typical ad hoc solution to this problem is to save intermediate files on
disk. Often the design of the computation itself takes several iterations as
intermediate steps are improved. Thus, some intermediate results need to be
recomputed. This involves a great amount of human management of the state of
the computation, breaking it up into pieces, and issuing jobs on the cluster.

@@

For example:

@@

Execution is the command used for running the tasks. It performs a more complex
version of the following pseudo-code:

@@

The \texttt{status} subcommand prints out a summary of the status of all of the
tasks. Figure~\ref{fig:jug-status-output} shows the output of this command
using the example jugfile above. We assume that the jugfile was called
\code{images.py} on disk and that there were 20~images in the directory. We can
see that there are 20~tasks ready to run, while the \code{mean} task is still
waiting for the results of the other tasks.

@@

It is still necessary to manually invalidate tasks. An alternative, would be to
take code which implements the task into account while computing the hash. This
would mark any results computed with this code as outdated if the code changed.
While this would add another layer of protection, it would still be possible to
make mistakes. If the function depended on other functions, especially if this
was done in a dynamic way, it could be hard to discover all dependencies (cf.\
sumatra~\footnote{Sumatra is a tool to collect all dependencies that are
necessary to run a particular computation. Its webpage is located at
\url{http://neuralensemble.org/trac/sumatra}.}). Additionally, even minute
refactoring of the code would lead to over eager recomputation. This could make
the developer wary of making improvements in their code, resulting in overall
worse code.
